Formalizing Commutative Algebra in Coq: \\ Nakayama's Lemma

### 2023-02-25 nakayama/paper.tex
Moved GitHub link to abstract

\begin{document}
\title[Formalizing Commutative Algebra in Coq]{ 
Formalizing Commutative Algebra in Coq: \\
Nakayama's Lemma\thanks{Source code for this work is available on the following
site: \url{https://github.com/ku-sldg/algebra}}
}

@@

\abstract{
  We describe our formal proof of Nakayama's Lemma, a fundamental theorem in
  the mathematical field of commutative algebra. The statement and proof of
  this result involve several commutative-algebraic structures including
  commutative rings, ideals of these rings, and modules over them, and we also
  explain our process of formalizing these structures.
}

>>>>

\begin{document}
\title[Formalizing Commutative Algebra in Coq]{ 
Formalizing Commutative Algebra in Coq: \\
Nakayama's Lemma
}

@@

\abstract{
  We describe our formal proof of Nakayama's Lemma, a fundamental theorem in
  the mathematical field of commutative algebra. The statement and proof of
  this result involve several commutative-algebraic structures including
  commutative rings, ideals of these rings, and modules over them, and we also
  explain our process of formalizing these structures. Source code for this
  work is available on the following site:
  \url{https://github.com/ku-sldg/algebra}.
}
